A new breeding crossover approach for evolutionary algorithms

### 2023-09-21 paper.tex
Proposal update

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.90\linewidth]{img/fig_grayscale_continuous.pdf}
        \caption{Black and white offspring, predictable color domain.} \label{fig.grayscale_continuous}
        \end{figure}

@@

>>>>

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.80\linewidth]{img/fig_grayscale_continuous.pdf}
        \caption{Black and white offspring, predictable color domain.} \label{fig.grayscale_continuous}
        \end{figure}

@@

    An exciting functionality of this strategy is that this new crossover operation will enable the offspring to continue exploring new search spaces with the birth of unique individuals. Because of the new values obtained within the parent's chromosome ranges, this technique will be helpful to avoid local optima stagnation by maintaining diversity due to the near-infinite possibility of stochastic values.

    Our proposed strategy is beneficial for evolutionary algorithms, where the individual's genetic code (or a similar data layout) is the main structure for storing the population information. It could also be valuable for other algorithms, such as Particle Swarm Optimization (PSO), in computing the new placement position caused by the movement of the particles.
